\begin{sidewaystable}[htbp]
    \centering
    \small
    \caption{Comparison of Numerical Conformal Mapping Methods}
    \label{tab:method_comparison}
    \renewcommand{\arraystretch}{1.5} % Good vertical spacing
    
    % The sum of the hsize values below MUST equal 7 (the number of columns)
    \begin{tabularx}{\textwidth}{@{} 
        >{\hsize=0.7\hsize\raggedright\arraybackslash}X  % 1. Method (Narrow)
        >{\hsize=0.7\hsize\raggedright\arraybackslash}X  % 2. Shape (Very Narrow)
        >{\hsize=0.6\hsize\raggedright\arraybackslash}X  % 3. Runtime (Narrow)
        >{\hsize=0.8\hsize\raggedright\arraybackslash}X  % 4. Input (Medium)
        >{\hsize=0.9\hsize\raggedright\arraybackslash}X  % 5. Output (Wide)
        >{\hsize=1.65\hsize\raggedright\arraybackslash}X % 6. Advantages (Very Wide)
        >{\hsize=1.65\hsize\raggedright\arraybackslash}X % 7. Disadvantages (Very Wide)
    @{}}
        \toprule
        \textbf{Method} & \textbf{$\Omega$ Shape} & \textbf{Runtime} & \textbf{Input} & \textbf{Output} & \textbf{Advantages} & \textbf{Disadvantages} \\
        \midrule
        
        \textbf{Schwarz-Christoffel} & 
        Polygon & 
        $\bigO(N^3)$ (parameter problem) & 
        Polygon vertices $z_k$ and angles $\theta_k$& 
        Integral parameters: prevertices $v_k$, $C$ & 
        Exact angle preservation at corner singularities; Handles unbounded \& periodic domains. & 
        Restricted to polygons; Crowding (resolution loss); Slow \\
        \addlinespace
        
        \textbf{Theodorsen} & 
        Star-shaped & 
        $\bigO(N \log N)$ & 
        Radial function $\rho(\theta)$ & 
        Boundary correspondence $\theta(\phi)$ & 
        Fast fixed-point iteration; Efficient FFT implementation. & 
        Restricted to star-shaped regions; Fails/Inaccurate for non-smooth boundaries or shapes far from $\disk$. \\
        \addlinespace
        
        \textbf{Zipper (Geodesic)} & 
        General Jordan incl. Fractals & 
        Fast, Dep. only on $N$ but not on shape & 
        Boundary points $\{z_i\}_{i\in[N]}$ & 
        Composition of elementary maps & 
        Robust (handles fractals); Finds inverse simultaneously. & 
        Expensive derivative computation (chain rule); Only approximates $\Gamma$. \\
        \addlinespace
        
        \textbf{Conjugate Function} & 
        General, incl. sharp corners/ cusps & 
        Dep. on mesh, slower than SC on polygons & 
        Boundary \& 4 marked vertices & 
        Conformal modulus $h$ \& $u,v$ potentials s.t. $\psi(z)=u(z)+ih(z)$ & 
        Exponential convergence using $hp$-FEM; Works on rough boundaries; Numerical stability thanks to dual BVP & 
        Point evaluation expensive (searching mesh) \\

        \textbf{Probabilistic} & 
        General, incl. Rough/ Fractals & 
        Polynomial & 
        Oracle / Boundary (pixel list) & 
        Random Walk approx. & 
        Works on rough boundaries where deterministic methods fail. & 
        Slow convergence; Inherent randomness; Difficult to guarantee accuracy. \\

        \textbf{Amano} & 
        Analytic & 
        $\bigO(N^3)$ & 
        Collocation points $z_i$ & 
        Lin. comb. of log potentials & 
        Fast linear point/derivative evaluation; Exponential accuracy; Simple implementation. & 
        Cannot use Fourier param. or mesh; Sensitive to charge point placement. \\
        \addlinespace
        
        \textbf{Wegmann (OAP)} & 
        Smooth & 
        $\bigO(N \log N)$ per iter.: FFT & 
        Fourier Series of $\eta$ & 
        Analytic Interpolating Polynomial & 
        Quadratic (fast) convergence for fine meshes; High accuracy (FFT); Efficient point evaluation. & 
        Requires good initial guess (local convergence); Requires smooth boundary. \\
        \addlinespace
        
        \bottomrule
    \end{tabularx}
\end{sidewaystable}